\cvsection{Experience}
\begin{cventries}
  \cventry
    {Graduate Student Researcher}
    {Centre for Complex Networks Research, Northeastern University}
    {Boston, USA}
    {Jan 2019 - Present}
    {
      \begin{cvitems}
        \item {Studying the effects of the linguistic structure of titles and abstracts of scientific publications in creating impact among \\ researchers, and building quantitative models to estimate it.}
        \end{cvitems}
    }
  \cventry
    {Data Scientist (Co-Op)}
    {Enterprise Risk - Analytics, Fidelity Investments.}
    {Boston, USA}
    {Jan 2018 - July 2018}
    {
      \begin{cvitems}
        \item {Analyzed network traffic log data, built insightful visualizations, and developed anomaly detection predictive models for abnormal network activity detection.}
        \item {Developed a framework for enhanced exploratory data analysis of network connection logs on PySpark2.}
      \end{cvitems}
    }
  \cventry
    {Senior Data Engineer}
    {Data Science Group, Innovation Labs, [24]7.ai Inc.}
    {Bangalore, India}
    {June 2016 - Dec 2016}
    {
      \begin{cvitems}
        \item {Modeled chat transcripts from customer conversations for user intent prediction for customer agent queue routing that achieved a recall of 0.87.}
        \item {Designed and developed a Natural Language toolkit on PySpark for chat transcript data analysis and modeling.}
        \item {Configured the toolkit on a multi-cluster environment with three apache spark nodes for scalability.}
      \end{cvitems}
    }
  \cventry
    {Data Engineer}
    {Data Science Group, Innovation Labs, [24]7.ai Inc.}  
    {Bangalore, India}
    {May 2015 - June 2016}
    {
      \begin{cvitems}
        \item {Analyzed and modeled user data from website visit behavior for several clients in the e-commerce domain for detection of potential customers who needed help with purchases and predicted their chat propensity with a customer service agent.}
        \item {Integrated SVM algorithm into the domain specific custom modeling tool and scaled over a million data points.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Xurmo Technologies Pvt. Ltd.}
    {Bangalore, India}
    {July 2011 - May 2015}
    {
      \begin{cvitems}
        %% \item {Developed and maintained machine learning modules of the flagship product of the company - Xurmo big data analytics platform.}
        \item {Developed custom analytical functions for Xurmo Big Data Platform for data transformation.}
        \item {Programmed analytics applications using Platform as a Service modules - Text exploration engine, Stock market movement prediction, Sentiment analyzer, Customer churn prediction.}
      \end{cvitems} 
    }
\end{cventries}
