
\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
%\usepackage[lf]{ebgaramond}
\usepackage[urw-garamond]{mathdesign}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeBullet}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeJobFunc}[2]{\resumeBullet{#1}{#2}\vspace{-0pt}}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://srjit.github.io/}{\Large Sreejith Sreekumar}} & Email: \href{mailto:sreekumar.s@husky.neu.edu}{sreekumar.s@husky.neu.edu}\\
  Portfolio: \href{http://srjit.github.io/}{http://srjit.github.io} & Mobile: +1-857-399-6443 \\ 
  Linkedin: \href{https://www.linkedin.com/in/srjit/}{https://www.linkedin.com/in/srjit/} & Github: \href{http://github.com/srjit}{http://github.com/srjit} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Boston, US}
      {Master of Science in Data Science}{Jan. 2017 -- Present}
    \resumeSubheading
      {Government Engineering College}{Thrissur, IN}
      {Bachelor of Technology in Computer Science and Engineering}{Sep. 2007 -- Apr. 2011}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
  \section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Specialities}
      {Classification and Clustering, Regression, Deep Learning, Natural Language Processing \& Distributed Computing}
    \resumeSubItem{Programming}
      {Python, R, Scala, Shell Scripting, Java, Groovy, Javascript}
    \resumeSubItem{ML Tools/Frameworks}
      {Tensorflow, Keras, Scikit-Learn, Pandas}
    \resumeSubItem{Big Data Ecosystem}
    {Apache Spark and Spark Mllib, Apache Hadoop, Hive, Flume, Sqoop, Oozie}
    \resumeSubItem{Databases}
      {MySQL, MongoDB, HP Vertica}
    \resumeSubItem{Certifications}
      {Scalable Machine Learning(edX), Introduction to Big Data with Apache Spark (edX), Machine Learning (Coursera)}
    
      \resumeSubHeadingListEnd

   %    -----------ACADEMIC PROJECTS-----------------

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Investigating Instances of Gun Violence using Pointer Networks}
      {Proposed a novel model that employs Attention Mechanism in Sequence-to-Sequence learning and Pointer Neural Nets to extract the attributes of gun violence events from news reports.}
    \resumeSubItem{Quantifying Semantic Similarity of Sentences using Long Short-Term Memory Networks}
      {Designed and implemented a sequence-to-sequence model (LSTM network) for classifying semantically similar and dissimilar questions from Quora, carrying an accuracy of 83\% on validation after tuning.}
    \resumeSubItem{Domain Specific Classification using AlexNet}
      {Tuned the layers of a pre-trained AlexNet model for binary classification task on images that obtained an accuracy 94\% for the new task.}
    \resumeSubItem{The Fake News Stance Classification}
    {Achieved an accuracy of 88\% on classifying fake news from the genuine ones to four discrete levels - agree, discuss, disagree, and unrelated using handcrafted linguistic features along with distance features from vectorized fields(Word2Vec). Random Forests, Support Vector Machines, and XGBoost algorithms were used for performance comparison.}
    \resumeSubItem{Home Value Prediction}
    {Modeled Zillow's house rent prediction problem using Microsoft's LightGBM algorithm with a mean absolute error of 0.064.}

  \resumeSubHeadingListEnd
      
  

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubHeadingListStart
    \resumeSubheading
      {Enterprise Risk - Analytics, Fidelity Investments}{Boston, US}
      {Data Scientist (Co-Op)}{Jan 2017 - Jul 2017}
      \resumeItemListStart
      \resumeJobFunc{}{Modeled the detection of anomalies in SOCKS proxy logs for suspicious network activity using Isolation Forest and \\Local Outlier Factor.}
      \resumeJobFunc{}{Developed a framework for enhanced exploratory data analysis of SOCKS connection logs on PySpark}
  %    \resumeJobFunc{}{Modeled the detection of anomalies in SOCKS proxy logs for suspicious network activity using Isolation Forest and Local Outlier Factor.}
      \resumeItemListEnd
      \resumeSubHeadingListEnd
      
\resumeSubHeadingListStart      
    \resumeSubheading
      {Data Science Group, Innovation Labs, [24]7.ai Inc.}{Bangalore, IN}
      {Senior Data Engineer}{Jun 2016 - Dec2016}
      \resumeItemListStart      
      \resumeJobFunc{}{Modeled chat transcripts from customer conversations for user intent prediction for customer agent queue routing that achieved an accuracy of ~90\%.}
      \resumeJobFunc{}{Designed and developed a Natural Language toolkit on PySpark for chat transcript data analysis and modeling.}
      \resumeJobFunc{}{Configured the toolkit on a multi-cluster environment with three apache spark nodes for scalability.}
      \resumeItemListEnd      
    \resumeSubHeadingListEnd        
      
\resumeSubHeadingListStart
    \resumeSubheading
      {Data Science Group, Innovation Labs, [24]7.ai Inc.}{Bangalore, IN}
      {Data Engineer}{May 2015 - June 2016}
      \resumeItemListStart            
       \resumeJobFunc{}{Analyzed and modeled user data from web for several clients in the e-commerce domain for increasing chat propensity of potential customers with customer agents and uplifting purchases.}
       \resumeJobFunc{}{Integrated SVM algorithm into the domain specific custom modeling tool and scaled over a million data points.}
      \resumeItemListEnd             
      \resumeSubHeadingListEnd        

\resumeSubHeadingListStart      
    \resumeSubheading
      {Xurmo Technologies Pvt. Ltd.}{Bangalore, IN}
      {Software Engineer}{July 2011 - May 2015}
      \resumeItemListStart            
       \resumeJobFunc{}{Developed and maintained machine learning modules of the flagship product of the company - Xurmo big data analytics platform.}
       \resumeJobFunc{}{Developed and integrated machine learning algorithms on Apache Spark (Java).}
       \resumeJobFunc{}{Developed custom analytical functions as a platform functionality for data transformation.}
       \resumeJobFunc{}{Programmed analytics applications using the Platform as a Service - Text exploration engine, Stock market movement prediction, Sentiment analyzer, Customer churn prediction.}
      \resumeItemListEnd             
      \resumeSubHeadingListEnd        


%
%      --------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}