\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Data Engineer}
    {[24]7 Innovation Labs}
    {Bangalore India}
    {June 2016 - Dec 2016}
    {
      \begin{cvitems}
        \item {Designed and developed a natural language toolkit on PySpark for chat transcript data analysis and modeling.}
        \item {Achieved an accuracy of 90\% in modeling chat transcripts and classifying them for user intent prediction.}
        \item {Configured and scaled the toolkit on a multi-cluster environment with three apache spark nodes.}
      \end{cvitems}
    }
  \cventry
    {Data Engineer}
    {[24]7 Innovation Labs}
    {Bangalore, India}
    {May 2015 - June 2016}
    {
      \begin{cvitems}
        \item {Analyzed and modeled user data from web for several clients in the e-commerce domain for increasing chat propensity and uplifting purchases.}
        \item {Integrated SVM algorithm into the domain specific custom modeling tool and scaled over a million data points.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {Xurmo Technologies Pvt. Ltd.}
    {Bangalore, India}
    {Feb 2012 - May 2015}
    {
      \begin{cvitems}
        \item {Developed and maintained machine learning modules of the flagship product of the company - Big data analytics platform.}
        \item {Developed and integrated machine learning algorithms on Apache Spark (Java).}
        \item {Developed HTTP based APIs for data retrieval and processing for the platform.}
        \item {Developed custom analytics functions for the engine data transformation.}
        \item {Wired up data ingestion and services APIs of the product.}
        \item {Built user interface for platform customers.}
        \item {Developed analytics applications on the platform - Text exploration engine, Stock market movement prediction, Sentiment analyzer, Customer churn prediction.}
      \end{cvitems} 
    }
  \cventry
    {Intern}
    {Xurmo Technologies Pvt. Ltd.}
    {Bangalore, India}
    {July 2011 - Feb 2012}
    {
      \begin{cvitems}
        \item {Implemented data collection modules for an enterprise knowledge discovery application.}
        \item {Collaborated for building data indexing and query optimization modules.}
      \end{cvitems} 
    }
\end{cventries}
